COG-ED Manuscript

### 2022-01-24 06_Paper/COG-ED/Manuscript.Rmd
added CI to footnote of tables
figure numbering is on point

keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, n-back"
wordcount         : "X"
bibliography      : CERED.bib
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : nature.csl
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
    - \usepackage[final]{pdfpages}

---

@@

  colnames(hypothesis1a_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
  hypothesis1a_contrasts$Contrast <- gsub("X", "", hypothesis1a_contrasts$Contrast)

@@

  colnames(hypothesis1b_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
  hypothesis1b_contrasts$Contrast <- gsub("X", "", hypothesis1b_contrasts$Contrast)

@@

  colnames(hypothesis1c_mental_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
  hypothesis1c_mental_contrasts$Contrast <- gsub("X", "", hypothesis1c_mental_contrasts$Contrast)
  colnames(hypothesis1c_physical_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
  hypothesis1c_physical_contrasts$Contrast <- gsub("X", "", hypothesis1c_physical_contrasts$Contrast)
  colnames(hypothesis1c_performance_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
  hypothesis1c_performance_contrasts$Contrast <- gsub("X", "", hypothesis1c_performance_contrasts$Contrast)
  colnames(hypothesis1c_effort_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
  hypothesis1c_effort_contrasts$Contrast <- gsub("X", "", hypothesis1c_effort_contrasts$Contrast)
  colnames(hypothesis1c_frustration_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
  hypothesis1c_frustration_contrasts$Contrast <- gsub("X", "", hypothesis1c_frustration_contrasts$Contrast)
  colnames(hypothesis1c_time_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
  hypothesis1c_time_contrasts$Contrast <- gsub("X", "", hypothesis1c_time_contrasts$Contrast)

@@

  # rename columns and contrasts for apa_print

  colnames(hypothesis2a_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
  hypothesis2a_contrasts$Contrast <- gsub("X", "", hypothesis2a_contrasts$Contrast)

@@

  h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.01)] <- 
    paste0(h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.01)],"*")
  h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.05)] <- 
    paste0(h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.05)],"*")
  h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.001)] <- 
    paste0("<.001***")

  h2b_result.table$`Random Effects (SD)`[3:6] <- paste0("")

@@

  h2c_ss.table$`$p$-value`  [which(h2c_ss.table$`$p$-value`<.01)] <- 
    paste0(h2c_ss.table$`$p$-value`[which(h2c_ss.table$`$p$-value`<.01)],"*")
  h2c_ss.table$`$p$-value`[which(h2c_ss.table$`$p$-value`<.05)] <- 
    paste0(h2c_ss.table$`$p$-value`[which(h2c_ss.table$`$p$-value`<.05)],"*")
  h2c_ss.table$`$p$-value`[which(h2c_ss.table$`$p$-value`<.001)] <- 
    paste0("<.001***")

@@

  h2c_ss.table$`$p$-value` <- str_replace(h2c_ss.table$`$p$-value`, "0.", ".")

@@

A sample size analysis with *G$\times$Power* [@Faul2007; @Faul2009], based on the results of the ANOVA of Westbrook et al. [-@Westbrook2013] which showed an increase in reaction time with higher n-back levels, indicated that we should collect data from at least 53 participants, assuming $\eta2=0.04$, $\alpha=.05$, and $\beta=.95$.
The power analyses of all other hypotheses yielded smaller necessary sample sizes.
To account for technical errors and exclusions of physiological data of the second lab session due to excessive noise, we aim to collect data of 60 to 70 participants.

@@

This research was partly funded by the German Research Foundation (DFG) as part of the Collaborative Research Center (CRC) 940.
The funders have/had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.
**OR**
The authors received no specific funding for this work.

@@

@@

```{r figure1appendix, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back > 3-back > 1-back."}

@@

@@

@@

`r apa_print(hypothesis1a_rmanova)$statistic`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1a_BF)$bf, digits = 2)`

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  hypothesis1a_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing $d'$ between n-back levels",
  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
  escape = FALSE,
  placement = "H"
)
```

@@

`r apa_print(hypothesis1b_rmanova)$statistic`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1b_rmanova$anova_table[1,"F"], df = hypothesis1b_rmanova$anova_table[1,"num Df"], df_error = hypothesis1b_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1b_rmanova$anova_table[1,"F"], df = hypothesis1b_rmanova$anova_table[1,"num Df"], df_error = hypothesis1b_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1b_BF)$bf, digits = 2)`

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  hypothesis1b_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing reaction time between n-back levels",
  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
  escape = FALSE,
  placement = "H"
)
```

@@

`r apa_print(hypothesis1c_mental_rmanova)$full_result`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1c_mental_rmanova$anova_table[1,"F"], df = hypothesis1c_mental_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_mental_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_mental_rmanova$anova_table[1,"F"], df = hypothesis1c_mental_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_mental_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1c_mental_BF)$bf, digits = 2)`

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_mental_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Mental subscale between n-back levels",
  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
  escape = FALSE,
  placement = "H"
)
```

@@

`r apa_print(hypothesis1c_physical_rmanova)$full_result`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1c_physical_rmanova$anova_table[1,"F"], df = hypothesis1c_physical_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_physical_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_physical_rmanova$anova_table[1,"F"], df = hypothesis1c_physical_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_physical_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1c_physical_BF)$bf, digits = 2)`

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_physical_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Physical subscale between n-back levels",
  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
  escape = FALSE,
  placement = "H"
)
```

@@

`r apa_print(hypothesis1c_time_rmanova)$full_result`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1c_time_rmanova$anova_table[1,"F"], df = hypothesis1c_time_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_time_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_time_rmanova$anova_table[1,"F"], df = hypothesis1c_time_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_time_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1c_time_BF)$bf, digits = 2)`

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_time_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Time subscale between n-back levels",
  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
  escape = FALSE,
  placement = "H"
)
```

@@

`r apa_print(hypothesis1c_performance_rmanova)$full_result`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1c_performance_rmanova$anova_table[1,"F"], df = hypothesis1c_performance_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_performance_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_performance_rmanova$anova_table[1,"F"], df = hypothesis1c_performance_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_performance_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1c_performance_BF)$bf, digits = 2)`

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_performance_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Performance subscale between n-back levels",
  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
  escape = FALSE,
  placement = "H"
)
```

@@

`r apa_print(hypothesis1c_effort_rmanova)$full_result`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1c_effort_rmanova$anova_table[1,"F"], df = hypothesis1c_effort_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_effort_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_effort_rmanova$anova_table[1,"F"], df = hypothesis1c_effort_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_effort_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1c_effort_BF)$bf, digits = 2)`

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_effort_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Effort subscale between n-back levels",
  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
  escape = FALSE,
  placement = "H"
)
```

@@

`r apa_print(hypothesis1c_frustration_rmanova)$full_result`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1c_frustration_rmanova$anova_table[1,"F"], df = hypothesis1c_frustration_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_frustration_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_frustration_rmanova$anova_table[1,"F"], df = hypothesis1c_frustration_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_frustration_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1c_frustration_BF)$bf, digits = 2)`

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_frustration_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Frustration subscale between n-back levels",
  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
  escape = FALSE,
  placement = "H"
)
```

>>>>

keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, n-back"
wordcount         : "X"
bibliography      : CERED.bib
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : nature.csl
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
    - \usepackage[final]{pdfpages}
    - \usepackage{chngcntr}

---
\renewcommand\thesection{\Alph{section}}
\counterwithout{figure}{section}
\setcounter{figure}{0}

@@

  colnames(hypothesis1a_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
  hypothesis1a_contrasts$Contrast <- gsub("X", "", hypothesis1a_contrasts$Contrast)

@@

  colnames(hypothesis1b_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
  hypothesis1b_contrasts$Contrast <- gsub("X", "", hypothesis1b_contrasts$Contrast)

@@

  colnames(hypothesis1c_mental_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
  hypothesis1c_mental_contrasts$Contrast <- gsub("X", "", hypothesis1c_mental_contrasts$Contrast)
  colnames(hypothesis1c_physical_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
  hypothesis1c_physical_contrasts$Contrast <- gsub("X", "", hypothesis1c_physical_contrasts$Contrast)
  colnames(hypothesis1c_performance_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
  hypothesis1c_performance_contrasts$Contrast <- gsub("X", "", hypothesis1c_performance_contrasts$Contrast)
  colnames(hypothesis1c_effort_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
  hypothesis1c_effort_contrasts$Contrast <- gsub("X", "", hypothesis1c_effort_contrasts$Contrast)
  colnames(hypothesis1c_frustration_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
  hypothesis1c_frustration_contrasts$Contrast <- gsub("X", "", hypothesis1c_frustration_contrasts$Contrast)
  colnames(hypothesis1c_time_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
  hypothesis1c_time_contrasts$Contrast <- gsub("X", "", hypothesis1c_time_contrasts$Contrast)

@@

  # get effect size and confidence intervals

  hypothesis2a_contrasts$etasq <- c(format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[1], df_error = hypothesis2a_contrasts$df[1], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[2], df_error = hypothesis2a_contrasts$df[2], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[3], df_error = hypothesis2a_contrasts$df[3], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[4], df_error = hypothesis2a_contrasts$df[4], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[5], df_error = hypothesis2a_contrasts$df[5], ci = 0.95), digits = 2)[1,1],
                                    format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[6], df_error = hypothesis2a_contrasts$df[6], ci = 0.95), digits = 2)[1,1])
  hypothesis2a_contrasts$CI <- c(format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[1], df_error = hypothesis2a_contrasts$df[1], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[2], df_error = hypothesis2a_contrasts$df[2], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[3], df_error = hypothesis2a_contrasts$df[3], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[4], df_error = hypothesis2a_contrasts$df[4], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[5], df_error = hypothesis2a_contrasts$df[5], ci = 0.95), digits = 2)[1,2],
                                 format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[6], df_error = hypothesis2a_contrasts$df[6], ci = 0.95), digits = 2)[1,2])

  colnames(hypothesis2a_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
  hypothesis2a_contrasts$Contrast <- gsub("X", "", hypothesis2a_contrasts$Contrast)

@@

  h2b_result.table$ `$p$-value`[which(h2b_result.table$ `$p$-value`<.01)] <- 
    paste0(h2b_result.table$ `$p$-value`[which(h2b_result.table$ `$p$-value`<.01)],"*")
  h2b_result.table$ `$p$-value`[which(h2b_result.table$ `$p$-value`<.05)] <- 
    paste0(h2b_result.table$ `$p$-value`[which(h2b_result.table$ `$p$-value`<.05)],"*")
  h2b_result.table$ `$p$-value`[which(h2b_result.table$ `$p$-value`<.001)] <- 
    paste0("<.001***")

  h2b_result.table$ `Random Effects (SD)`[3:6] <- paste0("")

@@

  h2c_ss.table$ `$p$-value`  [which(h2c_ss.table$ `$p$-value`<.01)] <- 
    paste0(h2c_ss.table$ `$p$-value`[which(h2c_ss.table$ `$p$-value`<.01)],"*")
  h2c_ss.table$ `$p$-value`[which(h2c_ss.table$ `$p$-value`<.05)] <- 
    paste0(h2c_ss.table$ `$p$-value`[which(h2c_ss.table$ `$p$-value`<.05)],"*")
  h2c_ss.table$ `$p$-value`[which(h2c_ss.table$ `$p$-value`<.001)] <- 
    paste0("<.001***")

@@

  h2c_ss.table$ `$p$-value` <- str_replace(h2c_ss.table$ `$p$-value`, "0.", ".")

@@

A sample size analysis with _G*Power_ [@Faul2007; @Faul2009], based on the results of the ANOVA of Westbrook et al. [-@Westbrook2013] which showed an increase in reaction time with higher n-back levels, indicated that we should collect data from at least 53 participants, assuming $\eta2=0.04$, $\alpha=.05$, and $\beta=.95$.
The power analyses of all other hypotheses yielded smaller necessary sample sizes.
To account for technical errors and exclusions of physiological data of the second lab session due to excessive noise, we aim to collect data of 60 to 70 participants.

@@

This research was partly funded by the German Research Foundation (DFG) as part of the Collaborative Research Center (CRC) 940.
The funders have/had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.

@@

\newpage
\setcounter{figure}{0}

@@

```{r figure1appendix, echo=FALSE, message=FALSE, warning=FALSE}

@@

*Figure 1* An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back > 3-back > 1-back.

@@

\counterwithin{figure}{section}
\setcounter{section}{19}
\setcounter{figure}{0}

@@

`r apa_print(hypothesis1a_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1a_BF)$bf, digits = 2)`

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  hypothesis1a_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing $d'$ between n-back levels",
  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

`r apa_print(hypothesis1b_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1b_rmanova$anova_table[1,"F"], df = hypothesis1b_rmanova$anova_table[1,"num Df"], df_error = hypothesis1b_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1b_rmanova$anova_table[1,"F"], df = hypothesis1b_rmanova$anova_table[1,"num Df"], df_error = hypothesis1b_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1b_BF)$bf, digits = 2)`

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  hypothesis1b_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing reaction time between n-back levels",
  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

`r apa_print(hypothesis1c_mental_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_mental_rmanova$anova_table[1,"F"], df = hypothesis1c_mental_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_mental_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_mental_rmanova$anova_table[1,"F"], df = hypothesis1c_mental_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_mental_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_mental_BF)$bf, digits = 2)`

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_mental_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Mental subscale between n-back levels",
  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

`r apa_print(hypothesis1c_physical_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_physical_rmanova$anova_table[1,"F"], df = hypothesis1c_physical_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_physical_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_physical_rmanova$anova_table[1,"F"], df = hypothesis1c_physical_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_physical_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_physical_BF)$bf, digits = 2)`

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_physical_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Physical subscale between n-back levels",
  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

`r apa_print(hypothesis1c_time_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_time_rmanova$anova_table[1,"F"], df = hypothesis1c_time_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_time_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_time_rmanova$anova_table[1,"F"], df = hypothesis1c_time_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_time_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_time_BF)$bf, digits = 2)`

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_time_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Time subscale between n-back levels",
  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

`r apa_print(hypothesis1c_performance_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_performance_rmanova$anova_table[1,"F"], df = hypothesis1c_performance_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_performance_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_performance_rmanova$anova_table[1,"F"], df = hypothesis1c_performance_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_performance_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_performance_BF)$bf, digits = 2)`

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_performance_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Performance subscale between n-back levels",
  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

`r apa_print(hypothesis1c_effort_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_effort_rmanova$anova_table[1,"F"], df = hypothesis1c_effort_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_effort_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_effort_rmanova$anova_table[1,"F"], df = hypothesis1c_effort_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_effort_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_effort_BF)$bf, digits = 2)`

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_effort_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Effort subscale between n-back levels",
  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

`r apa_print(hypothesis1c_frustration_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_frustration_rmanova$anova_table[1,"F"], df = hypothesis1c_frustration_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_frustration_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_frustration_rmanova$anova_table[1,"F"], df = hypothesis1c_frustration_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_frustration_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_frustration_BF)$bf, digits = 2)`

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_frustration_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Frustration subscale between n-back levels",
  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```
